\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2020-01-19 R1/Response.tex

	We thank the referee for their comments acknowledging the theoretical contributions of the paper.  While we believe that more theory focused papers lie within the scope of the International Journal of Forecasting, we also agree with the referee that the empirical section could be greatly improved.  We have endeavoured to do this in ways outlined in our responses below.\\

	\section*{Detailed Response to Referee 1: Major comments}

	\begin{enumerate}

		\item \textit{Lack of empirical contribution: The authors apply a couple of different transformations to the tourism data before constructing base forecasts. Failing to correctly transform the base forecasts back before they are reconciled introduces a bias. That the highest accuracy is obtained when applying the correct back-transformation is a very small contribution.}\\

		While agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.  However, we would like to emphasise that the extent to which it does this, also depend on the reconciliation method. TO DO (ELABORATE).\\

        \textit{When the authors introduce the log-transformation and in the graphs in Figures 6 and 7, they do not clarify the interplay between the transformation and the reconciliation constraints. If A + B = C then clearly $\log A + \log B = \log C$. In other words, a log-transformation affects the	reconciliation constraints. This needs to be explained more clearly; e.g., is the reconciliation constraint imposed on the transformed or the raw data?}\\

		TODO

		\textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\

### 2020-01-19 R1/Response.tex

	\begin{enumerate}

		\item \textit{Lack of empirical contribution: The authors apply a couple of different transformations to the tourism data before constructing base forecasts. Failing to correctly transform the base forecasts back before they are reconciled introduces a bias. That the highest accuracy is obtained when applying the correct back-transformation is a very small contribution.}\\

		While agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.  However, we would like to emphasise that the extent to which it does this, also depend on the reconciliation method. TO DO (ELABORATE).\\

        \textit{When the authors introduce the log-transformation and in the graphs in Figures 6 and 7, they do not clarify the interplay between the transformation and the reconciliation constraints. If A + B = C then clearly $\log A + \log B \neq \log C$. In other words, a log-transformation affects the	reconciliation constraints. This needs to be explained more clearly; e.g., is the reconciliation constraint imposed on the transformed or the raw data?}\\

		The observation regarding the constraints not holding on the log scale is correct.  When series are transformed to the log scale, forecasts are first produced on the log scale and these are back transformed to the original scale (possibly with bias correction) prior to carrying out reconciliation.  Therefore while all modelling is done on the log scale, all reconciliation is carried out on the original scale.  The fact that the constraints do not hold on the log scale is therefore not relevant.\\

		On re-reading the paper we do agree with the referee that there is scope for confusion here.  Therefore we have added some additional exposition to the beginning of section 4.1.  The aim here is to make it clear that after producing forecasting on some tranformed scale, the correct sequence of steps is to 1) back-transform to the original scale, 2) bias correct and 3) reconcile. \\

### 2020-01-19 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
extra exposition on linear constraints and log scale

Our own solution to dealing with biased forecasts is to bias correct \emph{before} reconciliation. In many cases the method for bias correction will be context specific. For instance, in our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking either a log transformation or a Box-Cox transformation before modelling. In this well-known case a number of bias correction methods exist based on Taylor expansions.

>>>>

Our own solution to dealing with biased forecasts is to bias correct \emph{before} reconciliation. In many cases the method for bias correction will be context specific. For instance, in our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where {\color{blue} data are modelled after} taking either a log transformation or a Box-Cox transformation. {\color{blue} Since linear constraints that hold on the original scale do not hold for the transformed series, back-transforming to the original scale is necessary.  Since this step induces a bias we propose to bias correct after this back-transformation step, and ultimately to reconcile the back-transformed, bias-corrected forecasts.}  In the well-known case {\color{blue} of the Box-Cox transformation} a number of bias correction methods exist based on Taylor expansions.
